The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-04-08 paper/iphas-dr2.tex

GB, JED and SES acknowledge support from the United Kingdom Science Technology and Facilities Council (STFC, JED and GB ST/J001333/1, SES ST/K00106X/1).
HJF is in receipt of an STFC postgraduate studentship.

>>>>

GB, JED, SES and BTG acknowledge support from STFC
(JED and GB ST/J001333/1, SES ST/K00106X/1, BTG ST/I001719/1). 
HJF is in receipt of an STFC postgraduate studentship.

BTG acknowledges funding from the
European Research Council under the European Union's Seventh Framework
Programme (FP/2007-2013) / ERC Grant Agreement n. 320964 (WDTracer).
